A Memory-Bounded, Deterministic and Terminating Semantics for the Synchronous Programming Language~\CEU

### 2018-02-23 03-semantics.tex
Refatora definições de \pot e \rank na 3.3.2

The main result of this section, Theorem~\ref{?}, is similar to
Theorem~\ref{thm.x.term-nst-*} but applies to transitions~$\trans$ in
general.  Therefore, before stating and proving it, we need to characterize
irreducible descriptions in general.

@@

  More formally,
  \[
    \pot(p,e)=\pot'(\bcast(p,e))\,,
  \]
  where~$\pot'$ is an auxiliary function that counts the number of
  reachable~$\ceu{\EmitInt}$ expressions in the program resulting from the
  broadcast of event~$e$ to~$p$.

@@

>>>>

The main result of this section, Theorem~\ref{?}, is similar to
Theorem~\ref{thm.x.term-nst-*} but applies to transitions~$\trans$ in
general.  Before stating and proving it, we need to characterize irreducible
descriptions in general, which depend on the notions of potency of a program
and rank of a description.

@@

  More formally, $\pot(p,e)=\pot'(\bcast(p,e))$, where~$\pot'$ is an
  auxiliary function that counts the number of reachable~$\ceu{\EmitInt}$
  expressions in the program resulting from the broadcast of event~$e$
  to~$p$.

@@

The next two lemmas establish that a single application of~$\out$ or~$\nst$
either preserves or decreases the rank of the input description.  All rank
comparisons assume lexicographical order.

\begin{lemma}\strut
  \label{lem.rank-out}
  \begin{enumerate}[(a)]
  \item\label{lem.rank-out-push} If~$\delta\outpush\delta'$
    then~$\rank(\delta)=\rank(\delta')$.
  \item\label{lem.rank-out-pop} If~$\delta\outpop\delta'$
    then~$\rank(\delta)>\rank(\delta')$.
  \end{enumerate}
\end{lemma}

\begin{lemma}
  \label{lem.rank-nst}
  %%
  If~$\delta\nst\delta'$ then~$\rank(\delta)\ge\rank(\delta')$.
\end{lemma}
